\documentclass[12pt,a4paper]{article}
\usepackage[top=1in, bottom=1.25in, left=1.25cm, right=1.25cm]{geometry}
%for vertically center the text in table box
\usepackage{array}
%for properly displaying urls in references
\usepackage{url}
%for gantt chart
\usepackage{pgfgantt}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\begin{document}

\title{Blind Assistance System}
\date{\today}
\author{Athul S Nambiar}

\pagenumbering{roman}
\center{}
\large{\textbf {GOVT. CCOLLEGE OF ENGINEERING, KANNUR}}
\newline
\large{\textbf {DEPT. OF COMPUTER SCIENCE AND ENGG}}
\newline
\newline
\newline
\newline
\LARGE{\textbf {\underline{MINI PROJECT PROPOSAL}}}
\large{}
\newline
\begin{flushleft}
	\begin{enumerate}
		\item {\bfseries Group Details With Email-ID And Mobile Numbers :}
		\newline
			\begin{tabular}{ | >{\centering\bfseries}m{1cm} | >{\raggedright}m{5cm} | >{\centering}m{6.5cm} | >{\centering\arraybackslash}m{3cm} | }
				\hline
				\textbf{Sl. No} & \textbf{Name} & \textbf{Email ID} & \textbf{Phone No} \\\hline
				1 & ALISHA SULTANA ALIYAR RAWTHER & alishu.sultana@gmail.com & 8592098264 \\\hline
				2 & ATHUL S NAMBIAR & athulsnambiarap@yahoo.com & 8111895136 \\\hline
				3 & SHAMILA MUSHTHAQUE & shamilamk@gmail.com & 7736380598 \\\hline
				4 & SHARANYA K V & sharanyakv96@gmail.com & 9497409820 \\\hline
				5 & SUJITH C P & sooji.sujith@gmail.com & 9747595727 \\\hline
			\end{tabular}
		\newline
		\item {\bfseries Title Of The Project :}\newline
		
		\begin{center}
			\textbf{BLIND ASSISTANCE SYSTEM}\hspace{20em}
			\textbf{Using Facial, Emotion \& Gender Recognition}
		\end{center}

		
		\item {\bfseries Abstract Of The Work :}
			\paragraph{} In today's world where humans are depending more and more on Artificial intelligence systems for various tasks, the complete interaction with an AI is not possible until the system knows the state of mind of human. And emotion is a very important feature for such interaction. Emotion can be judged from many aspects of human body such as facial expressions. Even the gender of a person can be recognised from their face image. Computers can be easily trained to extract emotions as well as gender information from facial images using image processing and machine learning. This system can be enhanced by adding face identification as well.
			\paragraph{} Such systems help blind people and people affected with autism to have better interaction in social life. Also, it has many applications in fields like marketing or E-Learning, where engagement of customers or students can be measured using emotions.		
			\newline
		\item {\bfseries Name Of The Guide :}\newline\newline
			\setlength{\parindent}{1cm}
			\indent {\bfseries Mr ASJAD NABEEL P }\newline
			\indent Asst. Professor Adhoc \newline
			\indent Computer Science Engineering \newline
			\indent Govt. College of Engg. Kannur \newline
			
		\item {\bfseries Objectives Of The Project : }
		\begin{itemize}
			\item To help blind people identify a person and recognise their emotion
			\item To create an application which can judge Emotions, Gender \& Identity of multiple faces from images or videos
			\item To add online learning ability to the application
		\end{itemize}
		
		\item {\bfseries Expected Final Outcomes : } \newline
		On successful completion of the project we will be able to ,
		\begin{itemize}
			\item Acquire skills in machine learning and image processing.
			\item Acquire professional skills in software development and management.
			\item Improve interaction skills.
			\item Achieve leadership quality.
		\end{itemize}
		
		\item {\bfseries Facilities Required : } \newline
		\setlength{\parindent}{1cm}
		\indent Access to project lab with personal Laptops
		
		
		\item {\bfseries Expected Expenditure, If Any : } No
		
		
		\clearpage
		
		\item {\bfseries Project Schedule : }
		
%			\begin{ganttchart}
%				[hgrid,
%				vgrid={*{6}{draw=none},dotted},,
%				time slot format = isodate,
%				x unit=0.12cm]{2016-07-22}{2016-10-25}
				
%				\gantttitlecalendar{month = name,day} \\
				
%				\ganttbar[bar/.append style={fill=blue}]{Dataset Collection}{2016-7-22}{2016-8-14} \\
%				\ganttbar[bar/.append style={fill=blue}]{Planning}{2016-7-22}{2016-8-14} \\
%				\ganttbar[bar/.append style={fill=blue}]{Development}{2016-8-15}{2016-9-15} \\
%				\ganttbar[bar/.append style={fill=blue}]{Testing}{2016-9-15}{2016-10-25} \\
%				\ganttbar[bar/.append style={fill=blue}]{Documentation}{2016-9-15}{2016-10-25}
				
%			\end{ganttchart}
		
		
		
			\begin{ganttchart}[hgrid,vgrid]{1}{24}
				\gantttitle{Project Schedule}{24} \\
				\gantttitle{July 22 - Aug 14}{8}
				\gantttitle{Aug 15 - Sept 15}{8}
				\gantttitle{Sept 15 - Oct 25}{8}\\
				
				\ganttbar[bar/.append style={fill=blue}]{Dataset Collection}{1}{8} \\
				\ganttbar[bar/.append style={fill=blue}]{Planning}{1}{8} \\
				\ganttbar[bar/.append style={fill=blue}]{Development}{9}{16} \\
				\ganttbar[bar/.append style={fill=blue}]{Testing}{17}{24} \\
				\ganttbar[bar/.append style={fill=blue}]{Documentation}{17}{24}
				
			\end{ganttchart}	
					
		
		\item {\bfseries References : }
			\bibliographystyle{unsrt}
			\nocite{kazemi2014one}
			\nocite{dalal2005histograms}
			\nocite{belhumeur1997eigenfaces}
			\nocite{ahonen2006face}
			\nocite{face}
			\nocite{gender}
			\bibliography{references}
	\end{enumerate}	
		\clearpage
		\pagenumbering{gobble}
		\begin{center}
			{\Large \textbf{Declaration by Group Members} }
		\end{center}
		
		\paragraph{} This proposal is submitted in partial fulfilment of the requirements for the B-Tech degree programme and we agree to complete the mini project work in accordance with the rules and regulations of the department.
		
		\paragraph{} Signature of members:
		
		\begin{enumerate}
			\item Alisha Sultana Aliyar Rawther
			\item Athul S Nambiar
			\item Shamila Mushthaque
			\item Sharanya K V
			\item Sujith C P \newline
		\end{enumerate}


		\begin{center}
			{\Large \textbf{Declaration by Project Guide} }
		\end{center}
		\paragraph{} This proposal has been submitted with my approval as the project guide and I am ready to guide the project work.\newline
		
		\textbf{Place : } GCE Kannur \hfill		\textbf{Name of the Guide:} ASJAD NABEEL P
		\newline
		\newline
		\textbf{Date  : }\today \hspace{7.5em} \textbf{Signature : }
		\newline
		\newline
		\newline
		

		\begin{center}
			{\Large\textbf{For Department Use Only}\hspace{20em}
		\textbf{Approved/Returned For Resubmission}}
		\end{center}



		\vspace{5em}
		\textbf{Signature} \hspace{10em}
		\textbf{Signature} \hspace{10em}
		\textbf{Signature}
		\newline
		\textbf{(Member)} \hspace{9.6em}
		\textbf{(Member)} \hspace{10.5em}
		\textbf{(HOD)}

		
		

\end{flushleft}

\end{document}
